LAGOS lake depth

### 2019-10-07 lagos_depth.Rmd
figure arrangement

```{r eval=TRUE, fig.height = 4}
cowplot::plot_grid(
  ggplot(data = hypso, aes(x = radius_percent, y = depth_percent)) +
    geom_point(aes(color = type)) + geom_line(aes(color = type)) +
    xlab("Radius distance (percent)") + ylab("Depth (percent)") + ylim(c(100, 0)), 
ggplot(data = hypso, aes(x = area_percent, y = depth_percent)) +
  geom_point(aes(color = type)) + geom_line(aes(color = type)) +
  xlab("Area > depth (percent)") + ylab("Depth (percent)") +
    ylim(c(100, 0))
)

@@

>>>>

```{r eval=TRUE, fig.height = 4}
cowplot::plot_grid(
  ggplot(data = hypso, aes(x = radius_percent, y = depth_percent)) +
    geom_point(aes(color = type)) + geom_line(aes(color = type)) +
    xlab("Radius distance (percent)") + ylab("Depth (percent)") + 
    ylim(c(100, 0)) +  theme(legend.position = "none"),
ggplot(data = hypso, aes(x = area_percent, y = depth_percent)) +
  geom_point(aes(color = type)) + geom_line(aes(color = type)) +
  xlab("Area > depth (percent)") + ylab("Depth (percent)") +
    ylim(c(100, 0)),
rel_widths = c(0.6, 1)
)

@@

```{r compare-slopes, eval=TRUE, fig.height = 4}
dt <- dplyr::filter(lg$lakes_limno,
                    !is.na(maxdepth) & !is.na(meandepth)) %>%
  dplyr::select(lagoslakeid, nhd_lat, nhd_long, maxdepth, meandepth) %>%
  dplyr::left_join(dplyr::select(lg$locus, lagoslakeid, lake_area_ha, gnis_name, state_zoneid)) %>%
  left_join(dplyr::select(lg$buffer100m.lulc,
                          buffer100m_slope_mean, lagoslakeid)) %>%
  dplyr::left_join(dplyr::select(lg$state, state_zoneid, state)) %>%
  dplyr::filter(lake_area_ha >= 4 & lake_area_ha <= 400) %>%
  dplyr::filter(state == "MN") %>%
  dplyr::filter(meandepth != maxdepth) %>%
  dplyr::filter(meandepth > 1)

# using lake areas:
# calculate a vector of lake radii
dt <- mutate(dt, radius = sqrt(lake_area_ha / pi))
# TODO: instead of straight-up radii use half the fetch or half the minimum bounding width
# Kath did geoprocessing using ArcGIS v 10.5 with tool Minimum Bounding Geometry in Features in Data Management Tools (System Toolbox)

# calculate "slopes" as max_depth / r
dt <- mutate(dt, slope = maxdepth / radius)

# calculate "half-slopes" as mean_depth / (r/2)
# how do they compare with full "slopes"?
dt <- mutate(dt, half_slope = meandepth / (radius / 2))

plot(dt$buffer100m_slope_mean, dt$slope)
abline(0, 1)
```

```{r eval=TRUE, fig.height = 4}
plot(dt$half_slope, dt$slope)
abline(0, 1)
```
